\documentclass[11pt]{amsart}
\usepackage{graphicx}
\usepackage{amsfonts,amsmath,amssymb,amsthm}
\usepackage{mathtools}
\usepackage[a4paper,margin=1in]{geometry} 
\usepackage{hyperref}
\usepackage{tikz}
\usetikzlibrary{positioning,calc}

% TODO
\hbadness=10000

\DeclarePairedDelimiter\norm{\lVert}{\rVert}
\DeclarePairedDelimiter\fracpart{\{}{\}}

\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\abs}[1]{\left|#1\right|}
\newcommand{\paren}[1]{\left(#1\right)}
\newcommand{\Int}[1]{\mathbb Z_{#1}}
\newcommand{\Unit}[1]{\Int{#1}^\times}

\newcommand{\R}{\mathbb{R}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Zko}{\Int{k+1}}
\newcommand{\Zp}{\Int{p}}
\newcommand{\rbf}{\mathbf{r}}
\newcommand{\abf}{\mathbf{a}}
\newcommand{\vbf}{\mathbf{v}}
\newcommand{\Vbf}{\mathbf{V}}
\newcommand{\ubf}{\mathbf{u}}
\newcommand{\Ubf}{\mathbf{U}}
\newcommand{\wbf}{\mathbf{w}}
\newcommand{\Wbf}{\mathbf{W}}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{claim}[theorem]{Claim}

\title{Eleven, twelve and thirteen lonely runners}
\author[T. Sungkawichai]{Touch Sungkawichai}
\date{\today}
\address{London, UK}
\email{touchsungkawichai@gmail.com}
\author[T. Trakulthongchai]{Tanupat Trakulthongchai}
\address{St John's College, University of Oxford, Oxford, UK}
\email{tanupat.trakulthongchai@sjc.ox.ac.uk}
\date{\today}
\subjclass[2020]{11K60}

\begin{document}
\maketitle
\begin{abstract}
    Wills stated the Lonely Runner Conjecture: if $k+1$ runners run with distinct and constant speeds around a unit circle from a 
    common starting point, each runner is at least $1/(k+1)$ away from every other runner at some point in time.
    A computational method developed by Rosenfeld and the second author verified the conjecture for up to $10$ runners.
    In this work, we provided computer-assisted proofs of the Lonely Runner Conjecture for $11$ and $12$ runners.
\end{abstract}

\section{Introduction}
The Lonely Runner Conjecture arose in the study of Diophantine approximation \cite{Wills},
though it has been interpreted in the context of view obstruction / Billiard trajectory 
\cite{cusick1984view}, covering radius of zonotopes \cite{henze_covering_2017}, and the chromatic number of a 
distance graph \cite{zhu2002circular}. 
It was conjectured independently by Wills \cite{Wills} in 1967 and Cusick\cite{cusick1984view} in 1984. 
In the most popular form, the conjecture asserts that if $k+1$ runners run with distinct,
constant speeds around a unit circle, each of them will be \emph{lonely} at some time. 
Here, a runner is said to be lonely if every other runner is at distance at least $\tfrac{1}{k+1}$ from them along the circle.

\begin{conjecture} \label{lonelyconj}
  Let $u_1,\ldots,u_{k+1}$ be distinct real numbers. There is a real number $t$ such that
  \[
    \norm{t u_i-tu_j} \ge \frac{1}{k+1} \quad \text{for all } i \neq j.
  \]
\end{conjecture}

The conjecture at each specific value of $k$ is called the Lonely Runner Conjecture for $k+1$ runners.
% Sidetrack? 
% Focusing on the distance of maximum loneliness, the lower bound of $\frac{1}{2k}$ follows immediately from the union bound. 
% Significant asymptotic improvements were due to Pararnau and Serra \cite{perarnau_correlation_2016}, Tao \cite{Tao}, 
% and lastly Bedert \cite{bedert_riesz_2025}, who, in November 2025, gave the present lower bound of 
% $\frac{1}{2k}+\frac{1}{k^{5/3+o(1)}}$.
%
% On the other hand, the conjecture has also been addressed from the ground up by proving it for small numbers of runners. 
% The conjecture is currently known to hold for $k+1\leq10$. From now on, we will restrict our attention to this direction;
% see the review of Perarnau and Serra \cite{perarnau_lonely_2025} for a broader perspective.

Lonely Runner Conjecture is currently known to hold for the cases of up to 10 runners.
The two smallest cases for $k$ are trivial. 
Betke~and~Wills~\cite{fourrunners} gave the proof for $k=3$ (the 4 runners case), 
and Cusick~and~Pomerance~\cite{cusick1984view} verified the conjecture for $k=4$ (the 5 runners case).
In the same paper that proved the case $k=5$, Bohman,~Holzman,~and~Kleitman~\cite{Bohman} showed that it suffices 
to consider integer speeds, transforming the problem from a continuous one to a discrete one. 
This reduction, combined with fixing the speed of the slowest runner to be $0$, produces the following
equivalent statement to Conjecture~\ref{lonelyconj}.

\begin{conjecture}
    Any $\ubf\in\Z_{>0}^k$ has the \emph{LR property}, that is, there is a real number $t$ such that
    \[\norm{tu_i}\geq\frac{1}{k+1} \quad \text{for all } i = 1,\dots,k+1.\] 
    
    We denote this statement by $LRC(k)$.
\end{conjecture}

To match with the conjecture's settings, we refer to the vector $\ubf = (u_1,\ldots,u_k)$ as a \emph{speed set} as 
it refers to the speed of the $k$ runners whose speed is nonzero.

Before 2025, the conjecture was known to be true for $k\leq6$, where the final case was proven by 
Barajas~and~Serra~\cite{barajas_lonely_2008} in 2008. In September 2025, Rosenfeld~\cite{Rosenfeld} introduced a computational 
method that settled $k=7$ (and later $k=8$ \cite{rosenfeld_lonely_2026}). In doing so, he relies on the finite-checking
result of Malikiosis, Santos, and Schymura~\cite{Malikiosis}, which follows from similar results of Tao~\cite{Tao} and
Giri~and~Kravitz~\cite{giri_structure_2026}. 
The~second~author~\cite{Trakulthongchai} subsequently refined this method to prove the conjecture for $k=8,9$ in November 2025.

In this paper, we further develop this computational method to verify the Lonely Runner Conjecture for $k=10$ and $11$. 
Our overall strategy is outlined in the next section where we provide more context of the computational method of \cite{Rosenfeld} 
and \cite{Trakulthongchai}. 
Section~\ref{sec:quotient}, \ref{sec:sieves} and \ref{sec:onetok} explain the techniques that help simplify the verification.
Section~\ref{sec:algo} summarizes the algorithm implemented, the results of which are presented in Section~\ref{sec:result}. 
Lastly, we discuss in Section~\ref{sec:further} how this method may be further extended. 

The article adopts following choices for notation: $\Int{n}$ denotes the additive group modulo $n$,
$\Unit{n}$ is the multiplicative group modulo $n$, and $\Int{n,l} = \Int{ln} \setminus n\Int{l}$
hence in particular $\Int{n,1}=\Unit{n}$.
Moreover, let $\pi_{m \to n}:\Int{m} \to \Int{n}$ denote the natural projection map when $n\mid m$
and $\pi_n: \Z \to \Int{n}$ denote the projection modulo $n$.
All scalar functions are also extended component-wise when applied with any vectors. 
For an operation $f$ on a set $S$ We may also write $fS$ to mean $\set{f(s) : s \in S}$. % to prevent polluting the article with parentheses.

\section{Overview}
We follow the computational framework laid by Rosenfeld~\cite{Rosenfeld}
and adopt some terminologies\footnote{
  Compared to \cite{Trakulthongchai}, the two main differences are replacing $I(k,l,p)$ with $I(k,p,l)$.
} and techniques from \cite{Trakulthongchai}.

Firstly, Rosenfeld reinterpreted the current best finite-checking result obtained by Malikiosis,~Santos,~and~Schymura~\cite{Malikiosis}:
\begin{lemma}[Corollary 3, \cite{Rosenfeld}] \label{ublemma}
    If $LRC(k-1)$ holds, then any counterexample $\ubf$ to $LRC(k)$ must have
    \[ u_1\cdots u_k < B_k \quad \text{where} \quad B_k := \paren{\frac{\binom{k+1}{2}^{k-1}}{k}}^k. \]
\end{lemma}

Hence, in order to verify $LRC(k)$, it suffices to check all positive integral speed sets such that $u_1 \cdots u_k < B_k$.
Rosenfeld then attacked this bound by generating multiple small proofs, each one asserts, for a particular prime $p$, 
that if $\ubf$ is a counterexample, then $p$ divides $u_1 \cdots u_k$. 
These small proofs are obtained computationally with the help of the following Lemma~\ref{divp}.

\begin{definition}[Definition 3.1, \cite{Trakulthongchai}] \label{def:improper}
    Let $p$ be a prime and $k,l$ be positive integers.
    A speed set $\vbf\in\Int{p,l}^k$ is $(k,p,l)$-\emph{improper} if both conditions hold: 
  \begin{itemize}
    \item for any $t \in \Int{lp}$ there exists $i$ such that $\norm{\frac{tv_i}{lp}} < \frac{1}{k+1}$.
    \item for all $i$, $\gcd(lp, v_1, \dots, \widehat{v_{i}}, \dots, v_k) = 1$.
  \end{itemize}
   If $\vbf$ is not improper, it is \emph{proper}. Moreover, let $I(k,p,l)$ denotes the set of all improper speed sets.
\end{definition}

One of the Rosenfeld's \cite{Rosenfeld} key insights is restricting time $t$ to be a rational number with denominator $lp$.
% one can apply this time solution to every speed set $\ubf$ such that $\pi_{lp}(\ubf) = \vbf$. 
% TODO: what are u, v

\begin{lemma}[Lemma 3.3, \cite{Trakulthongchai}] \label{divp}
    For $k\geq3$, if $LRC(k-1)$ holds and $I(k,p,l)$ is empty for some $l$, then any counterexample
    $\ubf$ to $LRC(k)$ satisfies $p \mid u_1 \cdots u_k$. 
\end{lemma}

Thus, by accumulating proofs of emptiness of $I(k,p,l)$ over a set of primes $P$, we obtain that $\prod_{p \in P} p$ 
divides $v_1\cdots v_k$. Therefore, if $\prod_{p \in P} p > B_k$, then there cannot be any counterexample to $LRC(k)$.

The main advance of \cite{Trakulthongchai} is the observation that allows $I(k,p,cl)$ to be computed efficiently as restated
\footnote{Notice that \text{shadow} in \cite{Trakulthongchai} is the preimage of the corresponding projection map} 
in Lemma~\ref{shadowing}.
% We define the \textit{shadow} of $\vbf\in\Int{p,l}^k$ to be the preimage of $\vbf$ in the projection from $\Int{clp}$ to $\Int{lp}$.
% Formally, $\delta_c=\pi^{-1}_{clp\to lp}$ in function terms.
% From this representation it is clear that indeed $\delta_c$ also depends on $p,l$ and implicitly $k$, 
% but we will use this as a shorthand and it will be clear in which domain our arguments live. 

\begin{lemma}[Lemma 3.5, \cite{Trakulthongchai}] \label{shadowing}
  For any $k, p, l, c$, the inclusion 
  \[ (\pi_{clp \to lp}) I(k,p,cl) \subseteq I(k,p,l) \]
  holds.
\end{lemma}

The following lemma enables the \emph{lifting} process of $I(k,p,l)$ to $I(k,p,cl)$ which is more fine-grained.
This lifting is done in hope that the extra structure of $\Int{clp}$ will help filtering out speed sets that cannot 
be a counterexample to the conjecture.
Lemma \ref{shadowing} motivates the definition of an \emph{eventually proper} speed set, 
which is the main subject of interest in our paper.
\begin{definition}
  \label{def:eventualproper}
  $\vbf \in \Int{p,1}^k$ is said to be \emph{eventually $(k,p)$-proper} if there is $l$ such 
  that \[ \vbf \notin (\pi_{lp \to p}) I(k, p, l) \]
\end{definition}

The concept of eventual properness simplifies our discussion and implementation; while many speed sets in $\Int{p,1}^k$ are not proper,
it is enough that they are all eventually proper.

\begin{lemma} \label{evenpropdivp}
  Let $k \ge 3$ and assume that $LRC(k-1)$ is true. If every $\vbf \in \Int{p,1}^k$ is eventually $(k,p)$-proper,
  then any counterexample $\ubf$ to $LRC(k)$ has $p \mid u_1\cdots u_k$.
\end{lemma}
\begin{proof}
  Since every $\vbf$ is eventually proper, it is possible to choose $l_\vbf$ to be an integer such that 
  \[ \vbf \notin (\pi_{l_\vbf p \to p}) I(k, p, l_\vbf) \]
  From there, pick $l$ to be the least common multiple of all the $l_\vbf$'s.
  By Lemma \ref{shadowing}, 
  \[ (\pi_{l_\vbf p \to p}) (\pi_{lp \to l_\vbf p}) I(k, p, lp) \subseteq (\pi_{l_\vbf p \to p}) I(k, p, l_\vbf p) \]
  Hence as $\vbf$ is not in the right hand side, it follows that, $\vbf \notin \pi_{lp \to p} I(k, p, lp)$.
  As this applies to all $\vbf$, it must follow that $I(k, p, lp)$ is empty, thus Lemma~\ref{divp} yields the needed conclusion. 
\end{proof}

\section{Quotient modulo prime} \label{sec:quotient}
The framework introduced in \cite{Trakulthongchai} has a bottleneck in the first phase of computation, namely,
the calculation of $I(k, p, 1)$. In this section, we aim to exploit the $\Unit{p}$ symmetry of $I(k,p,l)$ to reduce 
the amount of computation needed for $I(k, p, 1)$ and its subsequent lifts by a factor of $p-1$. 
Note that this reduces the computational complexity of checking $I(k,p,1)$ from $\Theta(p^k)$ to $\Theta(p^{k-1})$.

For a fixed $p$, consider the relation $\sim$ in $\Int{p,l}^k$ defined as
\[ \ubf \sim \vbf \iff \ubf = a\vbf \quad \text{for some } a\in\Unit{p}.\] 
It is easy to see that $\sim$ is an equivalence relation, but more importantly, this relation also preserves properness.

\begin{lemma} \label{lem:simpreserve}
Let $p,l\ge1$ and let $\ubf,\vbf$ be speed sets.
\begin{enumerate}
  \item If $\ubf \sim_{lp} \vbf$, then $\ubf$ is improper if and only if $\vbf$ is improper.
  \item If $\ubf \sim_p \vbf$, then $\ubf$ is eventually proper if and only if $\vbf$ is eventually proper.
\end{enumerate}
\end{lemma}

\begin{proof}
  Let $\ubf = a\vbf$ with $a \in \Unit{p}$.
\begin{enumerate}
  \item As $a$ is a unit, $a^{-1} \ubf = \vbf$ so 
  by symmetry, it suffices to show that improperness of $\vbf$ implies improperness of $\ubf$.
  Since $\gcd(a,p)=1$, it follows that  
  \[\gcd(lp, u_1, \dots, \widehat{u_i}, \dots, u_k) = \gcd(lp,av_1,\ldots,\widehat{av_{i}},\ldots,v_k) = \gcd(lp, v_1, \dots, \widehat{v_i}, \dots, v_k) = 1,\]
  thus the gcd condition of definition~\ref{def:improper} is preserved.
  Moreover, for any $t \in \Int{lp}$,
  \[ \norm{\frac{t u_i}{p}} = \norm{\frac{t(av_i)}{p}} = \norm{\frac{(at)v_i}{p}}, \]
  and since $at \in \Int{lp}$, the distance condition holds for $\ubf$ if and only if it holds for $\vbf$.
  Thus $\ubf$ is improper if and only if $\vbf$ is improper.

  \item Again, by symmetry, it suffices to show that $\ubf$ is eventually proper assuming $\vbf$ is.
  For simplicity, let $\pi := \pi_{lp\to p}$.
  As $\vbf$ is eventually proper, there exists $l$ such that $\vbf \not\in \pi I(k, p, l)$.
  In other words, $\pi^{-1}(\vbf) \cap I(k, p, l) = \emptyset$.
  Since the restriction $\pi^{-1} : \Unit{lp} \to \Unit{p}$ is surjective by the Chinese Remainder Theorem, 
  we may choose $b \in \Unit{lp}$ with $\pi(b) = a^{-1}$.

  For any $\ubf' \in \pi^{-1}(\ubf)$ we let $\vbf' = b\ubf'$. Then, 
  \[
    \pi(\vbf') = \pi(b)\pi(\ubf') = a^{-1}\ubf = \vbf,
  \]
  so $\vbf' \in \pi^{-1}(\vbf)$ and hence $\vbf' \notin I(k, p, l)$, so it is proper.
  By part (1), since $\vbf' \sim \ubf'$, $\ubf'$ is also proper.
  Thus $\pi^{-1}(\ubf)$ contains no improper speed set, which ensures that $\ubf$ is eventually proper.
\end{enumerate}
\end{proof}

Lemma~\ref{lem:simpreserve} implies that it is enough to concern only a single representative speed set in each equivalence class 
of $\sim$ when checking for the eventual properness. One easy way to pick a representative from each class in $\Int{p,1}^k$ 
is to keep the first coordinate fixed to $1$, which is what we chose for the implementation.

\section{Intermediate sieves} \label{sec:sieves}
In this section, we denote by $I'(k,p,l)$ and the quotient of $I(k, p, l)$ by $\sim$.
% (respectively $\Intbar{p,l}^k$) the quotient of $I(k,p,l)$ (respectively $\Int{p,l}^k$) by $\sim_p$. 
% For $l > 1$, we write $\ubf \sim_p \vbf$ to mean $\pi_{pl\to p}(\ubf)\sim_p\pi_{pl\to p}(\vbf)$.
% It is easy to see that any natural projection onto a multiple of $p$ preserves $\sim_p$ equivalence.

\subsection{Efficient Lifting}
One idea put forward by the second author in \cite{Trakulthongchai} was the insertion of an additional sieve.
Observe that the cost of lifting $I'(k,p,l)$ to $I'(k,p,cl)$ is proportional to \[ |I'(k,p,l)| \cdot c^k\] 
since each improper set modulo $lp$ has $c^k$ candidates (preimage modulo $clp$) that need verification.
When $k$ is large, the value of $c$ has greater impact on computation time. For example, for $k=11$, 
the $c=3$ lifts are almost 90 times more expensive than those with $c=2$.

As previously discussed, it is impossible to avoid lifting to a multiple of $k+1$; 
we have to go through all prime divisors of $k+1$ at least once.
Nevertheless, it is essential to carefully choose the order of each lift.
Since the $c=2$ lifts are cheap, performing them multiple times can help if they reduce the size of the search space,
i.e., if $|I'(k, p, 2l)| < |I'(k,p,l)|$.
Thus, employing a number of unneccessary cheap lifts before performing the more expensive and mandatory lifts, for example 
adding $c=2$ lifts before $c=3$ lifts, or adding $c=3$ lifts before $c=5$ lifts can shorten the overall computation time 
by reducing the amount of computation needed in larger modulus.

To put numbers to this observation, two example runs were conducted to illustrate this point. 
The first runs compare the proof for $k=8$. We define Scheme A as the method used in \cite{Trakulthongchai} and 
Scheme B to exploit the aforementioned lifting strategy.
To be specific, we use lifting diagrams to define the two schemes.

A lifting diagram always starts with $S_1=I'(k,p,1)$. A horizontal arrow pointing from $S_l$ towards $S_{cl}$ indicates a lift by multiplier $c$.
Vertical arrows indicate set operations. 
The process is always performed from top to bottom, and left to right. In this notation, Scheme A is just 
\begin{center}
  \begin{tikzpicture}[ node distance=1.5cm and 1.5cm, every node/.style={inner sep=2pt} ]
    \node (S1) {$S_1$};
    \node (S2) [right=of S1] {$S_2$};
    \node (S4) [right=of S2] {$S_4$};
    \draw[->] (S1) -- (S2);
    \draw[->] (S2) -- (S4);
  \end{tikzpicture}
\end{center}
and Scheme B is as follows:
\begin{center}
  \begin{tikzpicture}[ node distance=1.5cm and 1.5cm, every node/.style={inner sep=2pt} ]
    \node (S1) {$S_1$};
    \node (S2) [right=of S1] {$S_2$};
    \node (S4) [right=of S2] {$S_4$};
    \draw[->] (S1) -- (S2);
    \draw[->] (S2) -- (S4);

    \node (T1) [below=of S2] {$T_1$};
    \node (T3) [right=of T1] {$T_3$};
    \node (T9) [right=of T3] {$T_9$};
    \draw[->] (T1) -- (T3);
    \draw[->] (T3) -- (T9);

    \coordinate (M) at ($(S2)!0.5!(T1)$);
    \draw (S1) |- (M);
    \draw (S2) -- (M);
    \draw (S4) |- (M);

    \draw[->] (M) -- node[right=2pt] {$\min$} (T1);
  \end{tikzpicture}
\end{center}
where the operation min takes the smallest set among those joined by the arrow. 
To be more verbose, in this diagram, $S_l = I'(8,p,l)$ and $T_l=I'(8,p,lh)$ for some $h\in\{1,2,4\}$ depending 
on which $S_h$ is the smallest in certain case.

Using the same machine, Scheme A verifies the conjecture for $k=8$ in 18 seconds, while Scheme B takes 12 seconds.

The difference is more pronounced for $k=9$ where Scheme A is defined to be 
\begin{center}
  \begin{tikzpicture}[ node distance=1.5cm and 1.5cm, every node/.style={inner sep=2pt} ]
    \node (S1) {$S_1$};
    \node (S2) [right=of S1] {$S_2$};
    \node (S10) [right=of S2] {$S_{10}$};
    \draw[->] (S1) -- (S2);
    \draw[->] (S2) -- (S10);
  \end{tikzpicture}
\end{center}
and Scheme B is defined as
\begin{center}
\begin{tikzpicture}[ node distance=1.5cm and 1.5cm, every node/.style={inner sep=2pt} ]
    \node (S1) {$S_1$};
    \node (S2) [right=of S1] {$S_2$};
    \node (S4) [right=of S2] {$S_4$};
    \draw[->] (S1) -- (S2);
    \draw[->] (S2) -- (S4);

    \coordinate (MidS2S4) at ($(S2)!0.5!(S4)$);

    \node (T1) [below=1.5cm of MidS2S4] {$T_1$};
    \node (T3) [right=of T1] {$T_3$};
    \draw[->] (T1) -- (T3);

    \coordinate (MidT1T3) at ($(T1)!0.5!(T3)$);

    \node (U1) [below=1.5cm of MidT1T3] {$U_1$};
    \node (U5) [right=of U1] {$U_5$};
    \draw[->] (U1) -- (U5);

    \coordinate (M1) at ($(MidS2S4)!0.5!(T1)$);
    \draw (S2) |- (M1);
    \draw (S4) |- (M1);
    \draw[->] (M1) -- node[right=2pt] {$\min$} (T1);

    \coordinate (M2) at ($(MidT1T3)!0.5!(U1)$);
    \draw (T1) |- (M2);
    \draw (T3) |- (M2);
    \draw[->] (M2) -- node[right=2pt] {$\min$} (U1);

\end{tikzpicture}
\end{center}
In this case, it takes under 5 seconds to run Scheme B for a specidic $p=53$ while Scheme A does not finish in 15 minutes.

\subsection{Backward projection}

Just as lifting can reduce the size of the search space, projection can achieve a similar effect.
After computing $I'(k, p, l)$, projecting the speed sets back into $\Int{p}$ via the natural map $\pi_{pl \to p}$
can collapses several improper speed sets from $I'(k, p, l)$ into single representatives by maintaining only the structure 
in $\Int{p}$, discarding all other structures of $\Int{lp}$.
This action loses fine-grained detail of each improper speed set, but reduces the number of improper speed sets that need calculation.
Notice that $\abs{\pi_{pl \to p} S} \le \abs{S}$. The action of projecting a set down to $\Int{p}$ will be denoted 
as $\pi_{\to p}$ in the lifting diagram. 

This operation is legal because if a speed set $\vbf$ is not in the projected $\pi_{lp \to p} I'(k, p, l)$, then by Definition~\ref{def:eventualproper} 
and Lemma~\ref{lem:simpreserve}, it follows that $\vbf$ is eventually proper.
This fact implies that taking projection of a search space at any point will not skip over any speed sets.

\section{Eventual properness of
  \texorpdfstring{$(\pm1,\pm2,\ldots,\pm k)$}{(+/-1, +/-2, ..., +/-k)}
} \label{sec:onetok}
The high computational cost of lifting in the case $k=10$ motivates this section.
Although the exposition is tailored to $k=10$, the arguments apply more generally to any $k$
for which $k+1$ is prime.
With additional care in tracking divisibility conditions, most of the results can be extended
to the case where $k+1$ is not prime; however, the resulting conclusions are necessarily weaker.

We had observed that after lifting $I'(10, 1, p)$ with $c=2,3$ for a few times and consider the projection, 
the only speed sets in $I'(10, 1, p)$ that cannot be shown to be eventually proper are of the form 
\[ ( \pm1, \pm2, \ldots, \pm10 ).\]

It is unsurprising that these speed sets remain as they are lonely only at time $t=\frac{s}{11}$ for some $s \in \Z$ where
$11\nmid s$; what is perhaps surprising is that no other speed sets survive the pruning.
As mentioned, confirming that these speed sets are eventually proper requires a $c=11$ lift, which is relatively computationally expensive.
However, it is possible to exploit another structure of these speed sets to do so more efficiently.

% TODO: any reason why A? make it R? also can just defined down with rbf i think
Here, we write $\fracpart{x}$ for the fractional part of $x \in \R$ and let $A_n(x)=\lfloor n \fracpart{x}\rfloor$.
Equivalently, $A_n(x)$ is the number $k$ such that $\fracpart{x} \in [k/n, (k+1)/n)$, that is $A_n(x)$ refers to the
position on a unit cycle subdivided into $n$ parts,

We recall the following folklore result
\begin{lemma}[folklore]
\label{folklore}
    Suppose that $LRC(n)$ holds for all $n<k$. Let $p$ be a prime that divides $m$ speeds in $\vbf$, 
    where $\lceil\frac{2p}{k+1}\rceil<\frac{p}{k-m}$, and $\gcd(v_1,\ldots,v_k)=1$.
    Then $\vbf$ has the LR property.
\end{lemma}
\begin{proof}
  As $\vbf$ is treated as a set, reordering of elements does not lose any generality, thus we can assume that
  $v_1,\ldots,v_m$ are divisible by $p$ and $v_{m+1},\ldots,v_k$ are not. 
  Since $m<k$, $LRC(m)$ holds and there is a time $T \in \R$ when $\norm{Tv_i} \ge \frac{1}{m+1}$ for all $i\leq m$.
  
  By considering time of the form $t=T+\frac{r}{p}$ for $r \in \Zp$, we have that 
  \[ \norm{tv_i} = \norm{Tv_i} \ge \frac{1}{m+1} \quad \text{for all } i \le m \] as $p$ divides $v_i$. 
  For $i > m$, on the other hand, 
  \[ \set{ \fracpart*{(T + \frac{r}{p}) v_i} : r \in \Zp } = \set{ \fracpart*{Tv_i + \frac{r}{p}} : r \in \Zp } \]
  as multiplication by $v_i$ permutes elements in $\Zp$.

  Clearly, the latter set is the set of $p$ evenly spaced points on the unit circle, 
  so at most $\lceil\frac{2}{k+1}\cdot p\rceil$ points can intersect with the interval $\left(-\frac{1}{k+1},\frac{1}{k+1}\right)$. 
  In other words, at most $\lceil\frac{2p}{k+1}\rceil$ points are not lonely for each $i=m+1,\ldots,k$. 
    
  Since there are $k-m$ such indices, at most $(k-m) \lceil\frac{2p}{k+1}\rceil$ choices of $r\in\Zp$ are eliminated. 
  Hence if $(k-m) \left\lceil\frac{2p}{k+1}\right\rceil < p$, 
  then there must be a value of $r$ that makes $\norm{tv_i}\geq\frac{1}{k+1}$ for all $i\geq m+1$.
\end{proof}

\begin{definition}
\label{def:resolvable}
    Let $\vbf \in \Zko^k$ and $r \in \Zp$. 
    We write \[ \rbf(x)=\left(A_{k+1}(x), \; A_{k+1}(2x), \; \ldots, \; A_{k+1}(kx)\right) \] for $x\in\R$ and 
    say that $\vbf$ is $(k,p)$-\emph{resolvable} if any of the following holds:
    \begin{itemize}
        \item (scattered) $\vbf$ contains no zero component
        \item (divisible) $\vbf$ contains at least $\frac{k+1}{2}$ zero components
        \item (lonely) there is $s \in \Zko$ and $r \in \Zp$ for which
        \[ s\vbf + \rbf(r/p) \in \{1,\ldots,k-1\}^k\] when considered modulo $k+1$.
    \end{itemize}
    Let $J(k,p)$ be the set of speed sets that are not $(k,p)$-resolvable.
\end{definition}

% TODO easy !? please help me i'm too stupid
If not formally, at least intuitively, it is easy to see that this is just a reformulation of the previously
defined shadow of $(1,2,\ldots,k)$, and we can replace $(1,2,\ldots,k)$ with any $\wbf\in\Zp^k$ and change the definition
of the remainder vector analogously. The advantage of this formulation is that, by isolating $\rbf$ first, 
we can \emph{decouple} times of the form $t=\frac{q}{(k+1)p}$ to a partial fraction $t=\frac{s}{k+1}+\frac{r}{p}$ and only 
the first term influences the $a_ip$ term; the second term's effect is fully captured by $\rbf$. 
% TODO till here

Consequently, all dependence on $p$ has been eliminated except for that arising from $\rbf(\frac{1}{p} \Zp)$
in the lonely condition. As will be mentioned in \ref{corlarge}, even this dependence can be dropped when $p$ 
is sufficiently large.

We first argue that absense of non-resolvable speed sets entails that the speed set of the form $(\pm1, \pm2, \dots, \pm k)$
cannot be a counterexample.
\begin{lemma}
\label{lem:resolvable}
    Assume that $J(k,p) = \emptyset$ and $k+1$ is prime. Then $(\pm1,\pm2,\ldots,\pm k)$ is eventually $(k,p)$-proper.    
\end{lemma}
\begin{proof}
    First, we claim that $\vbf = (1,2,\ldots,k)$ is eventually proper. 
    Let $\ubf \in \Z^k$ be a preimage of $\vbf$ by $\pi_{p}$.
    By considering time of the form $t=\frac{s}{k+1}+\frac{r}{p}$ for $s\in\Zko$ and $r\in\Zp$, 
    the distance of the $i$-th runner from $0$ is given by
    \[ \fracpart{tu_i}=\fracpart*{\left(\frac{s}{k+1}+\frac{r}{p}\right) u_i}=\fracpart*{\frac{su'_i}{k+1}+\frac{ri}{p}} \] 
    where $\ubf' := (u'_1, \dots, u'_k) = \pi_{k+1} \ubf$.

    By assumption, $\ubf'$ is resolvable, thus one of the following case holds.
    \begin{itemize}
        \item $\ubf'$ is scattered. In this case, pick $r=0$ and $s=1$ and we have 
          \[ \fracpart{tu_i}=\fracpart*{\frac{u'_i}{k+1}} \]
          Since $u_i' \ne 0$, $\norm{tu_i} \ge \frac{1}{k+1}$ for all $i$.
          Hence $\ubf$ has the LR property.
        \item $\ubf'$ is divisible. Assume that $\ubf'$ contains $m \ge \frac{k+1}{2}$ zero components. 
          This precisely means that there are exactly $m$ coordinate of $\ubf$ that are divisible by $k+1$.
          By Lemma~\ref{folklore} with $p=k+1$ and $m \ge \frac{k+1}{2}$ 
          (note that the inequality
          \[\left\lceil \frac{2p}{k+1} \right\rceil = 2 < \frac{2(k+1)}{k-1} \leq \frac{p}{k-m}\] 
          holds),
          $\ubf$ has the LR property.
        \item $\ubf'$ is lonely.
          % TODO this is confusing
          There is a choice of $r$ and $s$ such that $ s\ubf' + \rbf(r/p) \in \{1,\ldots,k-1\}^k$ considered modulo $k+1$. 
          This means that $\fracpart{\frac{sv_i}{k+1}}=\frac{A_i}{k+1}$ and 
          $\fracpart{\frac{ri}{p}}\in\left[\frac{B_i}{k+1},\frac{B_i+1}{k+1}\right)$, where $C_i:=A_i+B_i\mod{k+1}$ 
          is in $\{1,\ldots,k-1\}$. Therefore,
          \[\fracpart{tu_i}=\fracpart*{\frac{su_i'}{k+1}+\frac{ri}{p}}\in\left[\frac{C_i}{k+1},\frac{C_i+1}{k+1}\right)\]
          and in particular the last set does not intersect $[0,\frac{1}{k+1})\cup(\frac{k}{k+1},1)$.  
          Since this holds for every $i$, $\ubf$ has the LR property.
          % END TODO
    \end{itemize}
    
    As all $\ubf$ in the preimage of $\vbf$ has the LR property, $\vbf$ must be eventually proper.
    
    Lastly, notice that for any $\vbf = (\pm 1, \pm 2, \dots, \pm k)$, the preimage $\ubf = (u_1, \dots, u_k)$ can be replaced 
    by $(u_1, \dots, -u_i, \dots, u_k)$ at any coordinate $i$ since $\norm{tu_i} = \norm{t(-u_i)}$, which completes the proof.
\end{proof}

Empirically, checking for emptiness of $J(k,p)$ is the most demanding step.
We show here that running this step once is conclusive for all sufficiently large $p$.

% TODO 
\begin{corollary}
    \label{corlarge}
    Suppose that $J(k,q)$ is empty for some prime $q$. 
    Then $(\pm1,\pm2,\ldots,\pm k)$ is eventually $(k,p)$-proper for every $p\geq k(k^2-1)$.
\end{corollary}
\begin{proof}
    Note that the only condition that depends on $p$ in Definition~\ref{def:resolvable} is the lonely condition. 
    Specifically, it only depends on $\rbf(\frac{1}{p}\Zp)$: if $\rbf(\frac{1}{q}\Z_q)\subseteq\rbf(\frac{1}{p}\Zp)$,
    then being $(k,q)$-happy is stronger than being $(k,p)$-happy.

    To show that this holds for any $p\geq k(k^2-1)$, we will show for such $p$, $\rbf(\frac{1}{p}\Zp)=\rbf([0,1])$.
    By pigeonhole, it suffices to show that the gaps between discontinuities in $\rbf([0,1])$ has length at least $1/p$
    because $\rbf$ only takes discrete value. Notice that $x\in[0,1]$ is a point of discontinuity only if $A_{k+1}(ix)\in\Z$ 
    for some $i\in\{1,\ldots,k\}$, that is $(k+1)ix=a$ for some $a\in\Z$. 
    Then if $x_1=\frac{a_1}{i_1(k+1)}$ and $x_2=\frac{a_2}{i_2(k+1)}$ are two distinct points of discontinuity with $x_1\neq x_2$ and
    $a_1,a_2,i_1,i_2$ integers, we have
    \[\begin{split}
        |x_1-x_2|&=\left|\frac{a_1}{i_1(k+1)}-\frac{a_2}{i_2(k+1)}\right|=\frac{1}{k+1}\left|\frac{a_1}{i_1}-\frac{a_2}{i_2}\right|\\ 
        &\geq\frac{1}{k+1}\cdot\frac{1}{k(k-1)}=\frac{1}{k(k^2-1)}\geq\frac{1}{p}.
    \end{split}\]

    Hence we conclude that $\rbf(\frac{1}{p}\Zp)=\rbf([0,1])$, and since $\frac{1}{q}\Z_q\subseteq[0,1]$, 
    we have the inclusion \[\rbf(\tfrac{1}{q}\Z_q)\subseteq\rbf([0,1])=\rbf(\displaystyle\tfrac{1}{p}\Zp).\]
    This shows that $J(k,p)$ is empty if $J(k,q)$ is empty, and the consequences follow from Lemma \ref{lem:resolvable}.
\end{proof}
% END TODO

\section{Algorithms for verification}
% TODO: without happy is already possible
% TODO: note that cor large is not used
\label{sec:algo}
From Lemmas \ref{evenpropdivp} and \ref{lem:simpreserve}, to show that $p\mid u_1\cdots u_k$ for any 
counterexample $\ubf$ to $LRC(k)$, it suffices to check that every speed set in $\Int{p,1}^k$ is eventually proper.

The lifting diagram for the case $k=11$ is
\begin{center}
    \begin{tikzpicture}[
    node distance=1.5cm and 1.5cm,
    every node/.style={inner sep=2pt}
]
    % Top Row (S nodes)
    \node (S1) {$S_1$};
    \node (S2) [right=of S1] {$S_2$};
    \node (S4) [right=of S2] {$S_4$};
    \node (S8) [right=of S4] {$S_8$};
    \node (S16) [right=of S8] {$S_{16}$};

    % Horizontal Arrows (with dotted last arrow)
    \draw[->] (S1) -- (S2);
    \draw[->] (S2) -- (S4);
    \draw[->] (S4) -- (S8);
    \draw[->, dotted] (S8) -- (S16); % Dotted arrow

    % Define merge points below the S nodes
    \coordinate (M4) at ($(S4)!0.5!(S4 |- 0,-2)$); % point below S4
    \coordinate (M8) at ($(S8)!0.5!(S8 |- 0,-2)$); % point below S8
    \coordinate (M16) at ($(S16)!0.5!(S16 |- 0,-2)$); % point below S16

    % Second Row (T nodes) starting centered under the merge
    % T1 is placed 1.5cm directly below S8 (the middle of the S4-S16 range)
    \node (T1) [below=1.5cm of S8] {$T_1$};
    \node (T3) [right=of T1] {$T_3$};
    \node (T9) [right=of T3] {$T_9$};

    % Define the merge horizontal line at y=-1cm relative to S row
    \draw (S4) |- (M8); % Line down and then to center
    \draw (S8) -- (M8);  % Direct line down
    \draw (S16) |- (M8); % Line down and then to center

    % Single arrow dropping to T1, with "min" label
    \draw[->] (M8) -- node[right=2pt] {$\min$} (T1);
    
    % Horizontal Arrows in Second Row
    \draw[->] (T1) -- (T3);
    \draw[->] (T3) -- (T9);

\end{tikzpicture}
\end{center}
The dotted arrow indicates that we only proceed to compute $S_{16}$ if the previous lift was productive,
that is, if $|I'(11,p,8)|<|I'(11,p,4)|$. Note that for most primes we did not have to compute $T_9$ because $T_3$ is already empty.
In any case, if $T_3$ or $T_9$ is empty, we conclude that $p$ divides the product $u_1\cdots u_k$ of a counterexample. 

The case $k=10$ is more involved. The goal of lifting here is not to show that the last set is completely empty, 
but that there are 10 equivalence classes of speed sets remaining, and in that case we know that they must be of the form
$(\pm1,\pm2,\ldots,\pm10)$. With this in mind, the lifting diagram in this case is as follows:
\begin{center}
    \begin{tikzpicture}[
    node distance=1.5cm and 1.5cm,
    every node/.style={inner sep=2pt}
]
    % Top Row (S nodes)
    \node (S1) {$S_1$};
    \node (S2) [right=of S1] {$S_2$};
    \node (S4) [right=of S2] {$S_4$};
    \node (S8) [right=of S4] {$S_8$};

    % Middle Row (T nodes) - Vertical spacing set to 1.5cm
    \node (T1) [below=1.5cm of S8] {$T_1$};
    \node (T3) [right=of T1] {$T_3$};
    \node (T9) [right=of T3] {$T_9$};

    % Define the midpoint between T1 and T9

    % Bottom Row (U node) - Vertical spacing set to 1.5cm
    \node (U1) [below=1.5cm of T9] {$U_1$};

    % Horizontal Arrows for S Row
    \draw[->] (S1) -- (S2);
    \draw[->] (S2) -- (S4);
    \draw[->] (S4) -- (S8);

    % Horizontal Arrows for T Row
    \draw[->] (T1) -- (T3);
    \draw[->] (T3) -- (T9);

    % Merge S1 and S8 down to T1
    \draw[->] (S8) -- node[right=2pt] {$\pi_{\to p}$} (T1);
    \draw[->] (T9) -- node[right=2pt] {$\pi_{\to p}$} (U1);

    \end{tikzpicture}
\end{center}

If $U_1$ contains $10$ elements, then we check that $J(10,p)$ is empty. 
If $J(10,p)$ is, from Lemma \ref{lem:resolvable} these remaining speed sets are eventually proper.

\section{Results}
\label{sec:result}
For the case $k=10$, let \[ P_{10} := \set{ \begin{aligned} 
    103, 131, 137, 139, 149, 151, 157, 107, 109, 127, 163, 167, 173, \\
    179, 433, 191, 193, 197, 199, 211, 223, 227, 229, 233, 239, 241, \\
    251, 257, 263, 269, 271, 277, 281, 283, 293, 307, 311, 313, 317, \\ 
    331, 337, 347, 349, 353, 359, 367, 373, 379, 383, 389, 401, 409, \\
    419, 421, 431, 433, 439, 443, 449, 457, 461 \\
    \end{aligned}
  } \]
and for the case $k=11$, let \[ P_{11} := \set{ \begin{aligned} 
      23, 131, 137, 139, 149, 151, 157, 163, 167, 173, 179, 181, 191, \\ 
      193, 197, 199, 211, 223, 227, 229, 233, 239, 241, 251, 257, 263, \\
      269, 271, 277, 281, 283, 293, 307, 311, 313, 317, 331, 337, 347, \\
      349, 353, 359, 367, 373, 379, 383, 389, 397, 401, 409, 419, 421, \\
      431, 433, 439, 443, 449, 457, 461, 463, 467, 479, 487, 491, 499, \\ 
      503, 509, 521, 523, 541, 547, 557, 563, 569, 571, 577 \\
    \end{aligned}
  } \]

Using the algorithms described in the previous section, we found that for $k\in\{10,11\}$ and $p\in P_k$, 
every $\vbf\in\Int{p,1}^k$ is eventually $(k,p)$-proper. 

\begin{theorem}
  The Lonely Runner Conjecture holds for $k=10$ and $k=11$.
\end{theorem}
\begin{proof}
  Recall that $LRC(k)$ holds for $k\leq 9$. By Lemma \ref{evenpropdivp} and the above computer verification, 
  any counterexample $\ubf$ to $LRC(10)$ must be divisible by \[\prod_{p \in P_{10}} p > e^{339} > e^{337.7} > B_{10}\] 
  where $B_{10}$ is the constant in Lemma \ref{ublemma}.
  But by the same lemma this is impossible, so no such $\ubf$ exists and $LRC(10)$ holds. 

  Similarly, for $k=11$, we also have
  \[ \prod_{p \in P_{11}} p > e^{435} > e^{434.5} > B_{11} \]
  and $LRC(11)$ follows.
\end{proof}

\subsection{Implementation details}
Rosenfeld wrote \cite{rosenfeldcode} to verify $k=7$ and the second author developed \cite{tanupatcode} to verify $k=8,9$. 
The latter code takes 
15 minutes for $k=8$ and approximately 23 hours for $k=9$. 
The first author developed \cite{mycode} to implement the algorithms in Section \ref{sec:algo}, with assistance from AI-based tools, 
to improve performance and scalability. In addition to the mathematical improvements described in Sections \ref{sec:quotient}, 
\ref{sec:sieves} and \ref{sec:onetok}, the practical aspect was also improved by refactoring the implementation to support parallel
execution and introducing more memory-efficient data structures.

These refinements dramatically improve runtime. Compared to the second author's original implementation in \cite{Trakulthongchai}, 
we proved $k=8$ in 12 seconds and $k=9$ in 181 seconds on a 10-core Apple M4 processor. 
The proofs of $k=10$ and $k=11$ were run in multiple batches, with multiple versions, and on multiple machines, 
thus making the exact time taken incomparable to other cases. The source of the computation, along with the log files, 
can be found in the first author's GitHub \cite{mycode}.

\section{Further work}
\label{sec:further}
It is feasible, via a natural extension of the algorithm for $k=10$, to verify the conjecture for $k=12$.
The main bottleneck in the case $k=12$ is verifying that $J(k,p)$ is empty which now takes 2 days for each $p$ on a 14-core
Apple M3 Max processor. The size of $\Z_{k+1}^k$ is $(k+1)^k$, and this constant when $k=12$ is $10^3$ times that when $k=10$.
Nonetheless, the case $k=12$ should be practically verifiable given enough computing resources.

For $k=13$, the main bottleneck will return back to the first phase of computation, but actually might even be "more possible"
and the $k=12$ variant. 

\bibliographystyle{amsplain}
\bibliography{ref}

\end{document}

